First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\ \large{Not For Distribution}

### 2020-05-13 paper/paper.tex
Bibliography/citations

@@

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

@@

@@

Tail recursion is given a direct-style representation using a simple sum type.

@@

This technique can be contrasted with the more traditional trampolining
technique for implementing tail recursion. Conventional trampolining uses a
sum type of the result type and a thunk with the code necessary to continue
execution.

\begin{todo}
  Cite "Trampolined Style" (S. E. Gantz, D. P. Friedman, M. Ward; 1999)
\end{todo}

@@

\begin{todo}
  Cite "Rewriting a Shallow DSL using a GHC Compiler Extension"
  (2017; Grebe, Young, Gill)
\end{todo}

@@

\section{Citations and Bibliographies}

\begin{todo}
  Fill in
\end{todo}

>>>>

\citestyle{acmauthoryear}

@@

%%
%% end of the preamble, start of the body of the document source.

\begin{document}

@@

Any data type with a \ttt{Generic} instance

@@

Tail recursion is given a direct-style representation using a simple sum type,
using the technique described in~\cite{Grebe:2017:RSD:3136040.3136048}.

@@

This technique can be contrasted with the more traditional trampolining
technique for implementing tail recursion. Conventional trampolining uses a
sum type of the result type and a thunk with the code necessary to continue
execution.~\cite{Ganz:99:Trampolined}

@@

@@

% \section{Citations and Bibliographies}

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}

% \begin{todo}
%   Fill in
% \end{todo}
